Fractional Types

### 2019-11-18 fracGC/p.tex
starting sec 3

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Preliminaries: Pi}
\label{sec:pi}

Our approach to reversible quantum programming based on type
isomorphisms. Examples.

Ancilla problem in the context of Pi using eta and epsilon 
informally.

%%%%%
\subsection{Pi}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Preliminaries: $\Pi$}
\label{sec:pi}

The step from reversible classical circuits to quantum circuits
requires the addition of just one gate that creates
superpositions. Similarly the step from a reversible classical
programming language to a quantum one requires just the management of
superpositions~\cite{10.1007/978-3-319-89366-2_19}. In the cited
paper, the core reversible classical language was Theseus~\cite{XXX},
a language that adds convenient syntactic extensions over an more
basic language $\Pi$ of combinators witnessing isomorphisms over
finite types~\cite{XXX}. The combinator-based language has the
advantage of being convenient for formal analysis for at least two
reasons: (i) it is conceptually simple and small, and (ii) it has
direct and evident connections to type theory and category
theory. Indeed our solution for managing ancillae is inspired by the
construction of \emph{compact closed categories}~\cite{XXX}. These
categories extend the monoidal categories~\cite{XXX} which are to
model most models of resource-aware programming languages~\cite{XXX}
with a new type constructor that creates duals or inverses to existing
types. This will be our fractional type.

%%%%%
\subsection{Core $\Pi$}
